Discrete Quantum Theories and Computing

### 2018-11-23 dissertation.tex
dissertation.lyx "Chapter 5 Further Discussion" Commented out...

To summarize, a conventional quantum probability measure has an uncountable
range $[0,1]$. A QIVPM constructed by blurring such a conventional
quantum probability measure must also have an uncountable range of
intervals. Of course, any particular QIVPM, or any particular experiment,
will use a fixed collection of intervals appropriate for the resources
and precision of the particular experiment.

\chapter{Further Discussion\label{chap:Further-Discussion}}

\todo{After updating Sec.~\ref{sec:fuzzy}, update this chapter
by starting from the meaning of Gleason's Theorem.} Almost all QIVPMs
in Chapter~\ref{chap:QIVPM} are closely related to quantum probability
measures. For example, given a $\delta$-deterministic QIVPM, Lemma~\ref{lemma:delta2zero}
provides a way to derive a $0$-deterministic QIVPM $\barmuD:\events\rightarrow\left\{ \imposs,\necess\right\} $
which is essential a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
satisfying $\mu\left(P\right)$ is either $0$ or $1$. Moreover,
an interval map $f:\left[0,1\right]\rightarrow\mathscr{I}$ in Sec.~\ref{sec:Gleason}
provides an systemic way to derive QIVPMs from quantum probability
measures.

the only QIVPM unrelated to quantum probability measures is defined
in Table~\ref{tab:non-Born-QIVPM}, and is ill-behaved as having
an empty core.

On one hand, classical IVPMs could be studied directly without deriving
from or to classical probability measures.

On the other hand, to state the original Gleason theorem, we don't
need to know a state a priori, and use this state to derive a quantum
probability measures and further a QIVPM. Therefore, it would be desirable
if we could answer the following variant of Gleason theorem which

whether shirking the maximum length of intervals alone could provide
a well-behaved QIVPMs. More precisely, we have the following question.

\begin{question}In a Hilbert space $\Hilb$ of dimension $D\geq3$,
given a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, $\alpha$
be the maximum length of intervals in $\mathscr{I}$, is there an
$\varepsilon\in\left(0,1\right)$ such that $\alpha<\varepsilon$
implies $\coreBorn\left(\bar{\mu},\events\right)\ne\emptyset$.\end{question}

>>>>

To summarize, a conventional quantum probability measure has an uncountable
range $[0,1]$. A QIVPM constructed by blurring such a conventional
quantum probability measure must also have an uncountable range of
intervals. Of course, any particular QIVPM, or any particular experiment,
will use a fixed collection of intervals appropriate for the resources
and precision of the particular experiment.\todo{Update the further
discussion chapter according to an updated Sec.~\ref{sec:fuzzy}.}
